---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# y2clerk

<!-- badges: start -->
<!-- badges: end -->


## Overview
`y2municipal` is the flagship package from Y2 Analytics to automate municipal reports. It relies heavily on other y2 packages, `y2clerk` and `orderlabel`, so be sure to have those installed first.

The goal of `y2municipal` is to quickly and easily go through the standard processes used in every municipal project of:

1) cleaning the voter file: 
2) weighting data: 
3) creating a topline report: `freqs_wuw()`, `topline()`
4) loading in data and y2 fonts: `read_data_names_fonts()`
5) creating visualizations: 



## Installation

<!-- You can install the released version of y2municipal from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("y2municipal") -->
<!-- ``` -->

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("nick-moffitt/y2municipal")
```


## Examples

Below you will find a few basic examples which show you how to quickly get a frequencies table with `freqs()`:

```{r example}
library(dplyr)
library(y2clerk)
library(orderlabel)
library(y2municipal)

# Run a weighted frequencies with unweighted ns
frequencies <- municipal_data %>%
  freqs_wuw(s_sex)

# Run a topline
DATA_PATH <- '~/Desktop/'
municipal_data %>% topline(weight_var = weights)
```


## Help
If you have issues using y2municipal, please post your issue on [GitHub](https://github.com/nick-moffitt/y2municipal/issues) along with a minimal reproducible example. We will do our best to address your issues and get them fixed for the next version of y2municipal. 

